%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Akshay Saxena}{ \\
\href{mailto:akshayonmailapp@gmail.com}{akshayonmailapp@gmail.com} | \text{$+91-9536634844$}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{APJ Abdul Kalam \\Technical University}

\descript{Bachelor of Technology in Computer Science}
\location{Aug-$2013$-May $2017$ }
Computer Science and Engg Dept.\\
BSA college of Engineering and Technology\\Mathura, Uttar Pradesh
\\
\location{ Max Pecent.: $82.45$ / $100.0$ \\
Overall Percent: $77.76$ / $100.0$  
 \ }
\sectionsep

\subsection{Amar Nath Vidya\\ Ashram,Mathura}
\location{Intermediate. April $2013$\\  Mathura,Uttar Pradesh\\Percentage :$86.04$/$100.0$}
\sectionsep
\subsection{Amar Nath Vidya\\ Ashram,Mathura}
\location{High School. April $2011$\\  Mathura,Uttar Pradesh
\\GPA :$9.80$/$10.0$}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
\begin{itemize}
\setlength\itemsep{0.01em}
\item Discrete Structure\\
\item Operating System\\
\item Data Structures \\
\item Design and Analysis of Algorithms \\
\item Database management system\\
\item Computer Networking \\
\item Compiler Designing\\
\item Automata Theory\\
\item Computer Organization\\
and Architecture\\
\end{itemize}
\sectionsep

%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\subsection{Programming}
\begin{itemize}
\setlength\itemsep{0.001em}
\item C \ \  \ \  \  \ \ \ \ \ \textbullet{} HTML
\item JAVA \ \ \textbullet{} CSS

\item JAVASCRIPT(L)
\item LaTeX \ \textbullet{} SQL
\end{itemize}
\location{Familiar:}
\textbullet{} Android \textbullet{} MySQL 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

\section{Projects}

\runsubsection{Proxy Catcher \ | Android-studio \ | JAVA \ | Jan-$2017$}\\
\descript{ Android based attendance managing application}
\begin{itemize}
\setlength\itemsep{0.001em}
\item A mobile based application for Android operating system that uses QR code of student to mark attendance.
\item Used ZXING LIBRARY better called as zebra crossing library to cipher various information present in QR code.
\item FIREBASE which is developed by GOOGLE is integrated in this application for authentication of user which support other functionalities as well and Analytics for tracking the progress of application.
\item Complete GUI of application is based on XML and used different font styles,drop down menus,lists etc.
\item Text to speech feature is enabled which provides complete detail about QR code after ciphering.
\end{itemize}
\sectionsep

\section{Training}
\runsubsection{Core Java | NEUMAN INSTITUTE (NICS) | MAY-$2015$} 
\begin{itemize}
\setlength\itemsep{0.001em}
      \item Trained at NICS Mathura centre for Core Java. 
    \item The main objective of this training is to learn various feature of JAVA as a programming language.
\end{itemize}

\section{Achievements and Awards}
\begin{itemize}
 \setlength\itemsep{0.001em}
\item Received certificate of appreciation from Mr.Kapil Sibal for outstanding performance in High school.
\item Certificate of achievement from APJ Abdul Kalam University for securing $1^{st}$ position in $"C"$ quiz competition.
\item Certificate of successful completion of training held by BARCLAY`S association with NASSCOM.
\end{itemize}
\section{Positions Held}
\begin{itemize}
\setlength\itemsep{0.001em}
    \item Technical Advisor at Erudition(BSA College-TechFest)\\
    Organized $2$ events and  Managed a team of $14$ students.
    \item College Representative for GLOBAL YOUTH EMPLOYABILITY INITIATIVE organized by GLOBAL TALENT TRACK.
    \item Headed a group of $8$ students to organize various placement drives successfully in pre-final year of college.
 \end{itemize}
\sectionsep
\section{Hobbies}
\begin{itemize}
\setlength\itemsep{0.001em}
\item Watching Documentaries.
\item Love to play Badminton.
\item Editing wikipages.
\item Solving puzzles.
\end{itemize}
\sectionsep
\end{minipage} 
\end{document}